QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-31 Response/Paper_Res.tex
Rev_V7.2

(b) Please note that for any queue in the system model, we assume that once a task is completed within a time slot, the next task in the queue will begin processing at the start of the next time slot. Besides, we assume that during each time slot, a mobile device either receives a new task or does not, considering the small duration of each time slot ($\tau = 0.1$ seconds). Based on these assumptions, in the previous version of the manuscript, we utilized the indicator function $\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)$ in Equations (21) and (22) to indicate edge server selection.
However, to address the reviewer’s comment and make the edge server selection more clear, we have included $y_{i,j}(t)$ into Equations (16) and (17) in Section III of the revised manuscript, as follows:

>>>>

(b) Please note that in the original version of the manuscript, we utilized the indicator function $\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)$ in Equations (21) and (22) to indicate edge server selection. Therefore, there was no need to include offloading indicator $y_{i,j}(t)$. However, to address the reviewer’s comment and make the edge server selection more clear, we have included $y_{i,j}(t)$ into Equations (16) and (17) in Section III of the revised manuscript, as follows:

%Please note that for any queue in the system model, we assume that once a task is completed within a time slot, the next task in the queue will begin processing at the start of the next time slot. Besides, we assume that during each time slot, a mobile device either receives a new task or does not, considering the small duration of each time slot ($\tau = 0.1$ seconds). Based on these assumptions, in the previous version of the manuscript, we utilized the indicator function $\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)$ in Equations (21) and (22) to indicate edge server selection.

### 2024-10-31 Revision/Paper_Rev.tex
Rev_V7.2

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

\item \textcolor{blue}{\textbf{DCDRL}~\cite{qiu2020distributed}: This method is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}. This method is designed for distributed computation offloading in a queuing-based MEC environment.} %We select DCDRL as a benchmark due to its similarity to our work.}

>>>>

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{red}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes~\cite{gao2022large}. We consider $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

\item \textcolor{red}{\textbf{DCDRL}~\cite{qiu2020distributed}: This method is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}. DCDRL is designed for distributed computation offloading in a queuing-based MEC environment.} %We select DCDRL as a benchmark due to its similarity to our work.}
